---
title: "Exercise 03"
author: "Hubert Rehrauer"
date: "28 09 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploratory Data Analysis

Do an exploratory data analysis of a matrix of expression values. The data consists of expression values for samples that were treated with DMSO and TSA. The samples were measured using three technologies: bulk, IFC96, IFC800. See the two RDS files `counts.RDS` and `phenodata.RDS`



## Data Import
```{r }
x = readRDS("counts.RDS")
anno = readRDS("phenodata.RDS")
head(anno)

```

## Compute and visualize basic statistics

How many replicates are there for each combination of factor levels?
How many genes have an expression value above 0 in each sample?

## Normalize the data
Scale the columns so that the total sum of all columns are identical


## Transform the data to log-scale

Use the function `log1p` to transform the data to log-scale



## Visualize the distribution of the expression values
Use violin plots and boxplots to visualize the distribution of the expression values
Group and color by experimental factors.

## Most variable genes

Identify the 500 most variable genes (with largest variance across samples) and continue working with those


## Sample correlations
Compute and visualize the sample-to-sample correlations

## Clustering
Compute and visualize a hierarchical clustering of the samples, use package `hclust`

## Heatmap
Use the package `pheatmap` to generate a heatmap of the expression data.

